---
title: "Homework 4"
author: "Kavya Chowti - kc45736"
date: "2024-02-15"
output: html_document
---

```{r global options,  echo=FALSE}
knitr::opts_chunk$set(fig.height=4, fig.width=7, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=60))
```

[Hyperlink to Github Repository]()

***

# **Question 1**

```{r echo=FALSE, message=FALSE}

# Load the data
gas_prices <- read.csv("GasPrices.csv")
attach(gas_prices)

```


#### **Theory A**
```{r echo=FALSE, message=FALSE, results='hide'}

# Subset data for stations with and without competitors
without_competitors <- gas_prices[gas_prices$Competitors == "N", "Price"]
with_competitors <- gas_prices[gas_prices$Competitors == "Y", "Price"]

# Calculate price difference
price_difference_A <- mean(without_competitors) - mean(with_competitors)

# Bootstrap resampling to compute confidence interval
price_diff_bootstrap_A <- replicate(10000, {
  without_competitors_sample <- sample(without_competitors, replace = TRUE)
  with_competitors_sample <- sample(with_competitors, replace = TRUE)
  mean(without_competitors_sample) - mean(with_competitors_sample)
})

# Compute confidence interval
price_diff_ci_A <- quantile(price_diff_bootstrap_A, c(0.025, 0.975))

# Results
price_difference_A
price_diff_ci_A


```

**Claim:** Gas stations without competitiors in sight charge more than those with competitors in sight

**Evidence:** There is no evidence to support the theory because when calculating the confidence interval for the difference in gas prices between gas stations with and without competitors in sight, the interval, (-0.009830686, 0.053708725), contains zero which means it is a plausible value for the difference in prices.

**Conclusion:** The theory is unsupported by the data as zero is a plausible value for the difference in prices between gas stations with and without competitors in sight meaning there is likely no difference as we are 95% confident the difference in prices falls within this interval. Therefore, the difference in price is not statistically significant.

#### **Theory B**

```{r echo=FALSE, message=FALSE, results='hide'}

library(mosaic)

# make a linear model since we are looking at correlation
gas_price_lm = lm(Price ~ Income, data = gas_prices)

# Bootstrap resampling to compute confidence interval
BootIncome = do(10000) * lm(Price ~ Income, data = resample(gas_prices))

# Compute confidence interval
price_diff_ci_b = confint(BootIncome, level = 0.95) %>%
  filter(name == "Income")
price_diff_ci_b

```

**Claim:** The richer the area or the higher the median houshold income within the area, the higher the gas prices.

**Evidence:** There is evidence to support the theory because when calculating the confidence interval for the difference in gas prices between gas stations with and without competitors in sight, the interval, (6.922364e-07, 1.760054e-06), does not contain zero. Based on the confidence interval, we can say that on average for every dollar increase in the median household income, the price of gas could increase anywhere from 6.922364e-07 to 1.760054e-06 dollars.

**Conclusion:** The theory is supported by the data as zero is most likely not a plausible value for the difference in prices between richer areas meaning there is likely a difference as we are 95% confident the difference in prices falls within this interval. Therefore, the difference in price is  statistically significant.

#### **Theory C**

```{r echo=FALSE, message=FALSE, results='hide'}

# Subset data for stations with and without stoplights
without_stoplights <- gas_prices[gas_prices$Stoplight == "N", "Price"]
with_stoplights <- gas_prices[gas_prices$Stoplight == "Y", "Price"]

# Calculate price difference
price_difference_C <- mean(with_stoplights) - mean(without_stoplights)

# Bootstrap resampling to compute confidence interval
price_diff_bootstrap_C <- replicate(10000, {
  without_stoplights_sample <- sample(without_stoplights, replace = TRUE)
  with_stoplights_sample <- sample(with_stoplights, replace = TRUE)
  mean(with_stoplights_sample) - mean(without_stoplights_sample)
})

# Compute confidence interval
price_diff_ci_C <- quantile(price_diff_bootstrap_C, c(0.025, 0.975))

# Results
price_difference_C
price_diff_ci_C


```

**Claim:** Gas stations that are located at stoplights charge more

**Evidence:** There is no evidence to support the theory because when calculating the confidence interval for the difference in gas prices between gas stations located at stoplights vs those not, the interval, (-0.03785923, 0.03182968), does contains zero which means it is a plausible value for the difference in prices.

**Conclusion:** The theory is unsupported by the data as zero is a plausible value for the difference in prices between gas stations located at stoplights vs those not meaning there is likely no difference as we are 95% confident the difference in prices falls within this interval. Therefore, the difference in price is not statistically significant.

#### **Theory D**

```{r echo=FALSE, message=FALSE, results='hide'}

# Subset data for stations with and without highway access
without_highway <- gas_prices[gas_prices$Highway == "N", "Price"]
with_highway <- gas_prices[gas_prices$Highway == "Y", "Price"]

# Calculate price difference
price_difference_D <- mean(with_highway) - mean(without_highway)

# Bootstrap resampling to compute confidence interval
price_diff_bootstrap_D <- replicate(10000, {
  without_highway_sample <- sample(without_highway, replace = TRUE)
  with_highway_sample <- sample(with_highway, replace = TRUE)
  mean(with_highway_sample) - mean(without_highway_sample)
})

# Compute confidence interval
price_diff_ci_D <- quantile(price_diff_bootstrap_D, c(0.025, 0.975))

# Results
price_difference_D
price_diff_ci_D


```

**Claim:** Gas stations that have direct highway access charge more than those without.

**Evidence:** There is evidence to support the theory because when calculating the confidence interval for the difference in gas prices between gas stations with and without direct highway access, the interval, (0.009338464, 0.080253308), does not contain zero. Based on the confidence interval, we can say that on average gas stations with direct highway access charge between $0.009338464 and $0.080253308 more compared to gas stations without durect access

**Conclusion:** The theory is supported by the data as zero is most likely not a plausible value for the difference in prices between gas stations with and without direct highway access meaning there is likely a difference as we are 95% confident the difference in prices falls within this interval. Therefore, the difference in price is statistically significant.

#### **Theory E**

```{r echo=FALSE, message=FALSE, results='hide'}

# Subset data for Shell and non-Shell gas stations
shell_prices <- gas_prices[gas_prices$Brand == "Shell", "Price"]
non_shell_prices <- gas_prices[gas_prices$Brand != "Shell", "Price"]

# Calculate price difference
price_difference_E <- mean(shell_prices) - mean(non_shell_prices)

# Bootstrap resampling to compute confidence interval for price differences
price_diff_bootstrap_E <- replicate(10000, {
  shell_prices_sample <- sample(shell_prices, replace = TRUE)
  non_shell_prices_sample <- sample(non_shell_prices, replace = TRUE)
  mean(shell_prices_sample) - mean(non_shell_prices_sample)
})

# Compute confidence interval
price_diff_ci_E <- quantile(price_diff_bootstrap_E, c(0.025, 0.975))

# Results
price_difference_E
price_diff_ci_E


```

**Claim:** Shell charges more than all other non-Shell brands

**Evidence:** There is no evidence to support the theory because when calculating the confidence interval for the difference in gas prices between Shell and non-Shell, the interval, 
(-0.009404334, 0.065617816), does contain zero which means it is a plausible value for the difference in prices.

**Conclusion:** The theory is unsupported by the data as zero is a plausible value for the difference in prices between Shell and non-Shell not meaning there is likely no difference as we are 95% confident the difference in prices falls within this interval. Therefore, the difference in price is not statistically significant.

# **Question 2**

```{r echo=FALSE, message=FALSE}

# load the dataset
sclass = read.csv("sclass.csv")
attach(sclass)

```

```{r echo=FALSE, message=FALSE, results='hide'}

# Load necessary libraries
library(dplyr)

# Part A: Filter the dataset for 2011 S-Class 63 AMGs
sclass_2011_63_AMG <- sclass %>%
  filter(year == 2011 & trim == "63 AMG")

# Define a function to compute bootstrap confidence intervals
boot_ci <- function(data, statistic, R=10000, alpha=0.05) {
  n <- length(data)
  boot_stats <- replicate(R, statistic(sample(data, replace=TRUE)))
  sorted_stats <- sort(boot_stats)
  lower <- sorted_stats[floor(R * alpha / 2)]
  upper <- sorted_stats[floor(R * (1 - alpha / 2))]
  return(c(lower, upper))
}

# Compute bootstrap confidence interval for average mileage
boot_mileage_ci <- boot_ci(sclass_2011_63_AMG$mileage, mean)

# Print the confidence interval
boot_mileage_ci

# Part B: Filter the dataset for 2014 S-Class 550s and create a new variable isBlack
sclass_2014_550 <- sclass %>%
  filter(year == 2014 & trim == "550") %>%
  mutate(isBlack = ifelse(color == "Black", TRUE, FALSE))

# Compute bootstrap confidence interval for proportion of black cars
boot_black_prop_ci <- boot_ci(sclass_2014_550$isBlack, mean)

# Print the confidence interval
boot_black_prop_ci

```

**95% Bootstrap CI of Average Mileage of 2011 S-Class 63 AMGs:**
(26274.24, 31711.82)

I am 95% confident that the average mileage for all 2011 S-Class 63 AMGs is between 26274.24 miles and 31711.82 miles.

**95% Bootstrap CI of Proportion of 2014 S-Class 550s Painted Black:**
(0.4164071, 0.4527518)

I am 95% percent confident that the proportion of all 2014 S-Class 550s that were painted black is between 41.64% and 45.28%.

# **Question 3**

```{r echo=FALSE, message=FALSE}

# load the dataset
nbc_pilotsurvey = read.csv("nbc_pilotsurvey.csv")
attach(nbc_pilotsurvey)

```

#### **PART A**
```{r echo=FALSE, message=FALSE, results='hide'}

# Filtered dataset for "Living with Ed" and "My Name is Earl"
filtered_data_a <- nbc_pilotsurvey %>%
  filter(Show %in% c("Living with Ed", "My Name is Earl"))

# Calculate mean responses for each show
mean_happy <- filtered_data_a %>%
  group_by(Show) %>%
  summarize(mean_response = mean(Q1_Happy))

# Conduct t-test for difference in mean responses
t_test <- t.test(Q1_Happy ~ Show, data = filtered_data_a)

# Calculate confidence interval for the difference in mean responses
ci_happy <- t_test$conf.int
ci_happy


```

**Question:** Which show makes people happier: "Living with Ed" or "My Name is Earl"?

**Approach:** To answer this question, since we are looking at a difference in means for a "large sample" I am going to use the t.test function in R as t tests are used primarily for means and for sample where CLT applies.

**Results:** Based on the t-test, the confidence interval that was computed is (-0.1030341, 0.4011371). Since zero is  within the interval there is no evidence that one show makes viewers happier than the other.

**Conclusion:** The question, does one show make viewers happier than the other is unsupported by the data as zero is  a plausible value for the difference in Q1_Happy question responses meaning it is not likely there is a difference and the difference is not statistically significant. Based on the confidence interval we are 95% confident that the difference in mean happiness responses for the shows "Living with Ed" and "My Name is Earl" and is between -0.1030341 to 0.4011371 This means the mean happiness response for the show "Living with Ed" is anywhere between 0.1030341 less to 0.4011371 more than "My Name is Earl".

#### **PART B**

```{r echo=FALSE, message=FALSE, results='hide'}

# Filtered dataset for "The Biggest Loser" and "The Apprentice: Los Angeles"
filtered_data_b <- nbc_pilotsurvey %>%
  filter(Show %in% c("The Apprentice: Los Angeles", "The Biggest Loser"))

# Calculate mean responses for each show
mean_annoyed <- filtered_data_b %>%
  group_by(Show) %>%
  summarize(mean_response = mean(Q1_Annoyed))

# Conduct t-test for difference in mean responses
t_test <- t.test(Q1_Annoyed ~ Show, data = filtered_data_b)

# Calculate confidence interval for the difference in mean responses
ci_annoyed <- t_test$conf.int
ci_annoyed

```

**Question:** Which show makes people more annoyed: "The Biggest Loser" or "The Apprentice: Los Angeles"?

**Approach:** To answer this question, since we are looking at a difference in means for a "large sample" I am going to use the t.test function in R as t tests are used primarily for means and for sample where CLT applies.

**Results:** Based on the t-test, the confidence interval that was computed is (0.01743792, 0.52455614). Since zero is not within the interval there is evidence that one show makes viewers happier than the other.

**Conclusion:** The question, does one show make viewers more annoyed than the other is supported by the confidence interval as zero is not in the interval meaning there is likely a difference and the difference is statistically significant. Based on the confidence interval we are 95% confident that the show "The Apprentice: Los Angeles" has a 0.01743792 to 0.52455614 higher mean annoyance response compared to "The Biggest Loser" and consistently produces a higher annoyance response among viewers.

#### **PART C**

```{r echo=FALSE, message=FALSE, results='hide'}

# Filtered dataset for "Dancing with the Stars"
filtered_data_c <- nbc_pilotsurvey %>%
  filter(Show == "Dancing with the Stars")

# Calculate proportion of responses of 4 or greater to "Q2_Confusing"
proportion <- mean(filtered_data_c$Q2_Confusing >= 4)

# Calculate confidence interval for the proportion
ci_confused <- prop.test(sum(filtered_data_c$Q2_Confusing >= 4), nrow(filtered_data_c))$conf.int
ci_confused

```

**Question:** What proportion of American TV watchers would we expect to give a response of 4 or greater to the Q2_Confusing question meaning that they agreed the show "Dancing With the Stars" is a confusing show?

**Approach:** To answer this question, since we are looking at a proportion of the population for a "large sample" I am going to use the prop.test function in R as proportion tests are used primarily for samples where CLT applies.

**Results:** Based on the proportion-test, the confidence interval that was computed is (0.04453431, 0.12893254). 

**Conclusion:** Based on the confidence interval we are 95% confident that for the show "Dancing With the Stars", on average 4.45% to 12.89% of viewers would give a response of 4 or higher to the Q2_Confused question.

# **Question 4**

```{r echo=FALSE, message=FALSE}

ebay = read.csv("ebay.csv")
attach(ebay)

```

```{r echo=FALSE, message=FALSE, results='hide'}

# Load necessary libraries
library(dplyr)

# Compute revenue ratio
ebay <- ebay %>%
  mutate(rev_ratio = rev_after / rev_before)

# Compute difference in revenue ratio between treatment and control groups
treatment_rev_ratio <- ebay %>%
  filter(adwords_pause == 1) %>%
  summarize(mean_rev_ratio = mean(rev_ratio))

control_rev_ratio <- ebay %>%
  filter(adwords_pause == 0) %>%
  summarize(mean_rev_ratio = mean(rev_ratio))

diff_rev_ratio <- treatment_rev_ratio$mean_rev_ratio - control_rev_ratio$mean_rev_ratio

# Bootstrap with 10,000 Monte Carlo simulations
set.seed(123) # for reproducibility
n_simulations <- 10000

bootstrap_diff <- replicate(n_simulations, {
  treatment_sample <- sample(ebay$rev_ratio[ebay$adwords_pause == 1], replace = TRUE)
  control_sample <- sample(ebay$rev_ratio[ebay$adwords_pause == 0], replace = TRUE)
  mean(treatment_sample) - mean(control_sample)
})

# Compute 95% confidence interval
ci_ebay <- quantile(bootstrap_diff, c(0.025, 0.975))

# Print results
ci_ebay


```

**Question:** What is the difference in revenue ratio between the treatment and control DMAs for EBay, and is this difference statistically significant?

**Approach:** I first computed the revenue ratio for each DMA, then calculated the difference in revenue ratio between treatment and control groups. To assess statistical significance, I used bootstrapping with at 10,000 Monte Carlo simulations to construct a 95% confidence interval for the difference in revenue ratio.

**Results:** Based on my bootstrapping simulation, the confidence interval that was computed is (-0.09137524, -0.01294320) which suggests that the revenue ratio in treatment DMAs is lower compared to control DMAs. 

**Conclusion:** The confidence interval provides evidence that there is a statistically significant difference in revenue ratio between treatment and control DMAs. It indicates that turning off paid search advertising in treatment DMAs may have negatively impacted eBay's revenue. This suggests that paid search advertising on Google's platform may actually create extra revenue for eBay, as turning off advertising resulted in a lower revenue ratio in the treatment group. Therefore, it may be beneficial for eBay to continue investing in paid search advertising to maintain or increase revenue levels.


